Gender, Age, and Peer Influence on Food Incentives in Schools

### 2024-02-20 outputs/paper/paper.qmd
added next steps

Being that the study was undertaken in a low-income neighborhood in Chicago, when introducing the incentive factor in the public treatment, the spillover effect may be magnified as these elementary students may be more influenced to alter their final food choice and choose the incentivized grapes. As this study took place in a low-income neighbourhood in Chicago, IL, it is rewasonable to say that this study was conducted in a socio-cultural vaccum. Compared to students surveyed in more affluent neighborhoods who may not be as swayed by the option of a prize, students in the state of Chicago qualify for free lunch because their annual household income is below the poverty line--the impact of this socio-economic experience cannot be captured in a study of such nature, nor a study of such size (diminutive compared to the scale of the impact of the lived experience). Students could have been making decisions based off of food scarcity, resource scarcity, peer pressure, fear of judgement, fear of authority, so on and so forth. So, while it is completely fair to judge the results of the original study for what they are, it is not ethical to make assumptions or inferences about *why* students make the decisions they make with regard to this study, without a comparison study or a larger data set to anchor statistics across demographics outside of Chicago, or outside of this specific school. Ultimately, it is unequivocally impossible to account for and measure every variable which influenced the students' decision-making, incentivized or not.

Regardless of the nature of the decision-making, it is clear that incentivization works. Looking toward the future, we may consider: how do we leverage incentivization to produce large-scale results and changes in behaviour? For instance, if the balh balh balh

>>>>

Being that the study was undertaken in a low-income neighborhood in Chicago, when introducing the incentive factor in the public treatment, the spillover effect may be magnified as these elementary students may be more influenced to alter their final food choice and choose the incentivized grapes. Compared to students surveyed in more affluent neighborhoods who may not be as swayed by the option of a prize, students in the state of Chicago qualify for free lunch because their annual household income is below the poverty line--the impact of this socio-economic experience cannot be captured in a study of such nature, nor a study of such size (diminutive compared to the scale of the impact of the lived experience). Students could have been making decisions based off of food scarcity, resource scarcity, peer pressure, fear of judgement, fear of authority, so on and so forth. So, while it is completely fair to judge the results of the original study for what they are, it is not ethical to make assumptions or inferences about *why* students make the decisions they make with regard to this study, without a comparison study or a larger data set to anchor statistical results across demographics outside of Chicago, or outside of this specific school. Ultimately, it is unequivocally impossible to account for and measure every variable which influenced the students' decision-making, incentivized or not.

Regardless of the nature of the decision-making, it is clear that incentivization works. For our next step, it is essential to consider how we can leverage incentivization to produce significant changes in behaviour on a large scale. For example, we can design reward programs that encourage people to adopt healthy habits or participate in eco-friendly practices.
To test the effectiveness of incentivization across different age groups, we may need to conduct the same study with various demographic groups. This will enable us to determine whether there are any differences in how people respond to incentives based on their age or other factors. For instance, younger people may be more motivated by incentives related to technology, while older generations may be more motivated by financial incentives.
